Electricity Markets

### 2023-05-11 presentations/power_slides.tex
updates

\logo{
   \tikz [remember picture,overlay]
    \node[yshift=.3cm,xshift=1.5cm] at (current page.south west)
        %or: (current page.center)
        {\includegraphics[width=1in]{UA-ASB-COLOUR.png}};
%\includegraphics[height=0.8cm]{UA-ASB-COLOUR.png}\vspace{220pt}
}

@@

\institute[2017]
{
  Alberta School of Business, University of Alberta
 }

@@

\begin{frame}
   \tikz [remember picture,overlay]
    \node[yshift=-0.95cm,xshift=0cm] at (current page.north)
        %or: (current page.center)
        %\node[yshift=-0.75cm,xshift=4.5cm] at (current page.north west)
        %{\includegraphics[width=3in]{UA-ASB-COLOUR.png}};
        {\includegraphics[width=\paperwidth]{EE_logo.png}}; \vspace{1cm}
   \titlepage
   \vfill
\end{frame}

@@

\begin{frame}{Price Volatility}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
        {\includegraphics[width=.9\paperwidth]{../images/peak_prices_2000_2019.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{New Technology}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
        {\includegraphics[width=.9\paperwidth]{../images/brooks_solar.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{tabular}{p{\linewidth}}
    \centering
    \includegraphics[width=.9\linewidth]{grid_ess.png} \\[\abovecaptionskip]
  Source: \url{http://www.mpoweruk.com/grid_storage.htm}
\end{tabular}

@@

\begin{frame}{Prices over time}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
        {\includegraphics[width=.9\paperwidth]{../images/peak_prices_2000_2019.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{The Balancing Pool: What on earth does it do?}
\vspace{-.2cm}\centering
\hspace{-1.5cm}\begin{tabular}{p{1.1\linewidth}}
    \centering
    \includegraphics[width=.9\linewidth]{balancingpool.png} \\[\abovecaptionskip]
  Source: Capital Power
\end{tabular}

>>>>

\logo{
   \tikz [remember picture,overlay]
    \node[yshift=.3cm,xshift=1.5cm] at (current page.south west)
        %or: (current page.center)
        {\includegraphics[width=1in]{UA-COLOUR.png}};
%\includegraphics[height=0.8cm]{UA-ASB-COLOUR.png}\vspace{220pt}
}

@@

\institute[2017]
{
  Department of Economics and Faculty of Law, University of Alberta
 }

@@

\begin{frame}
   \tikz [remember picture,overlay]
    \node[yshift=-0.5cm,xshift=-1.7cm] at (current page.north east)
        %or: (current page.center)
        %\node[yshift=-0.75cm,xshift=4.5cm] at (current page.north west)
        %{\includegraphics[width=3in]{UA-ASB-COLOUR.png}};
        {\includegraphics[width=1in]{UA-COLOUR.png}}; \vspace{1cm}
   \titlepage
   \vfill
\end{frame}

@@

\begin{frame}{Price Volatility}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
        {\includegraphics[width=.9\paperwidth]{../images/prices_and_loads.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

@@

\begin{tabular}{p{\linewidth}}
    \centering
    \includegraphics[width=.9\linewidth]{../images/grid_ess.png} \\[\abovecaptionskip]
  Source: \url{http://www.mpoweruk.com/grid_storage.htm}
\end{tabular}

@@

\begin{frame}{Prices over time}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
        {\includegraphics[width=.9\paperwidth]{../images/prices_and_loads.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{The Balancing Pool: What on earth does it do?}
\vspace{-.2cm}\centering
\hspace{-1.5cm}\begin{tabular}{p{1.1\linewidth}}
    \centering
    \includegraphics[width=.9\linewidth]{../images/balancingpool.png} \\[\abovecaptionskip]
  Source: Capital Power
\end{tabular}
